### 2020-08-31 LaTeX/sections/paper.tex
Paper - Updates on the tables and text

\subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways. We can use the \texttt{SELFDESTRUCT} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract). Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller. Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list. Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results the in the less final net cost due to the 24000 gas refunds. Also, it is best to avoid storing unnecessary storage variables on chain. Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing the highest priority element from the two implementations of sorted linked lists that contain 50 unsigned integers.

@@

\subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways. For dequeuing items from this priority queue we can use the \texttt{DELETE} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with15,000 refunded~\cite{wood2014ethereum}. So although the \texttt{DELETE} method refunds in 15000 gas, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction. In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority items and not delete the mapping element associated with the previous pointers. As it can be seen in Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas to dequeue 50 unsigned integers from this priority queue with respect to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.

@@

%  = = = = = = = = = = %

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Clearing the Mapping Elements}}         			& 38 pairs                					& 5,372,679                   				& 457,326,935                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Destroying the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %

@@

@@

\section{Clearing Mappings}

@@

\section{Closing and Reopening the Market}

>>>>

\subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways. We can use the \texttt{SELFDESTRUCT} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract). Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller. Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list. Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results in the less final net cost due to the 24000 gas refunds. Also, it is best to avoid storing unnecessary storage variables on chain. Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing highest priority elements in the two implementations of sorted linked lists that contain 50 unsigned integers.

@@

\subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways. For dequeuing items from this priority queue we can use the \texttt{DELETE} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with 15,000 refunded~\cite{wood2014ethereum}. So although the \texttt{DELETE} method refunds in 15000 gas, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction. In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority item and not delete the mapping element associated with the previous pointers. As it can be seen in the last two columns of Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas for dequeuing 50 unsigned integers compared to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.

@@

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Clearing the Mapping Elements}}         			& 86 pairs                					& 5,433,259                   				& 62,774,170                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Destroying the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %

\end{tabular}
\caption{\footnotesize{}
\label{tab:LLMApping_worst_case_matching}}
\end{table}

@@

\section{Call Market Different Design and Implementation Details }

@@

\subsection{Clearing Mappings}

@@

\subsection{Closing and Reopening the Market}
